Effectful Semantics for Substructural SSA

### 2023-11-16 pldi24/paper.tex
Alas for POSIX!

As a concrete example, we can now introduce the \textbf{printing monad}, which
is simply defined as \(\ms{Print}\;A \equiv \ms{Traces}\;\Sigma\), where
\(\Sigma: (\ms{Bytes}^*)^\omega \to \ms{Bytes}^{\leq \omega}\) denotes
concatenation of lists of bytestrings. This can be equipped with the structure
of a substructural effectful category by choosing \(M_C = M_R = \{[]\}\), giving
us an \isotopessa model supporting the instructions \(\ms{print} \in
\mc{I}^\varnothing_0(\ms{Bytes}, \mb{1})\) and \(\ms{rand} \in
\mc{I}^\taff_1(\mb{1}, A)\) for \(A\) nonempty, with standard semantics
\(\dnt{\ms{print}} = \lambda b.\{\iota_0 ((), [b])\}\), \(\dnt{\ms{rand}} =
\lambda (). \{\iota_0 (a, p[]) \mid a \in A\}\).

@@

  \item \(\ms{print}: \mc{I}^\varnothing_0((\ms{Bytes}, \ms{emp}), (\mb{1},

>>>>

As a concrete example, we can now introduce the \textbf{printing monad}, which
is simply defined as \(\ms{Print}\;A \equiv \ms{Traces}\;\Sigma\), where
\(\Sigma: (\ms{Byte}^*)^\omega \to \ms{Byte}^{\leq \omega}\) denotes
concatenation of bytestrings into a potentially infinite bytestream. This can be
equipped with the structure of a substructural effectful category by choosing
\(M_C = M_R = \{[]\}\), giving us an \isotopessa model supporting the
instructions \(\ms{print} \in \mc{I}^\varnothing_0(\ms{Byte}^*, \mb{1})\) and
\(\ms{rand} \in \mc{I}^\taff_1(\mb{1}, A)\) for \(A\) nonempty, with standard
semantics \(\dnt{\ms{print}} = \lambda b.\{\iota_0 ((), b)\}\),
\(\dnt{\ms{rand}} = \lambda (). \{\iota_0 (a, []) \mid a \in A\}\).

@@

  \item \(\ms{print}: \mc{I}^\varnothing_0((\ms{Byte}^*, \ms{emp}), (\mb{1},
